A mechanism to control synchronization in coupled area-preserving maps

### 2018-08-29 Syncarea_control/Syncarea_control.tex
sync area code + plot
syncarea tex updated

\begin{document}
\title{A mechanism to control synchronization in coupled area-preserving maps}
\affiliation{Department of Physics, Indian Institute of Technology Madras, Chennai, 600036, India.}
\author{Swetamber Das}
\email{swetdas@physics.iitm.ac.in}
\affiliation{Department of Physics, Indian Institute of Technology Madras, Chennai, 600036, India.}
%\author{Neelima Gupte}
%\email{gupte@physics.iitm.ac.in}
%\affiliation{Department of Physics, Indian Institute of Technology Madras, Chennai, 600036, India.}

\begin{abstract}
\pacs{05.45.+b}
\end{abstract}
\maketitle

>>>>

\begin{document}
\title{A mechanism to control synchronization in coupled area-preserving maps}
\affiliation{Department of Physics, Indian Institute of Technology Madras, Chennai, 600036, India.}
\author{Swetamber Das}
\email{swetdas@pks.mpg.de}
\affiliation{Max Planck Institute for the Physics of Complex Systems \\ 
N\"othnitzer Stra\ss e 38, Dresden, Germany.}
%\author{Neelima Gupte}
%\email{gupte@physics.iitm.ac.in}
%\affiliation{Department of Physics, Indian Institute of Technology Madras, Chennai, 600036, India.}

\begin{abstract}
    A unidirectionally coupled area-preserving maps with mixed phase space may 
    show identical synchronization in the sticky neighborhood of the regular 
    islands. We use this fact to devise a couple of numerical procedures to 
    delay and expedite the process of synchronization in standard maps coupled 
    under  Pecora-Caroll scheme. The delay method is based on controlled 
    kicking of trajectories away from the regular islands for as long as 
    necessary. On the other hand, the method to expiate the process is
    achieved by a parameter perturbation technique which rapidly drives the 
    chaotic trajectories to synchronization traps in the sticky neighborhoods 
    of regular islands. We also point out of limitations of these methods. 
\pacs{05.45.+b}
\end{abstract}
\maketitle
